Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-24 manuscript/manuscript.tex
Modified analytical solutions for spherical shell in manuscript
Modified linear density in manuscript

For future purposes we are going to obtain the gravity potential for 
three different functions from the perspective of their variation in 
$r'$: a linear and an exponential density function.
\todo[inline]{lo sacaria}

@@

We have computed these gravitational fields on every point of the four 
grids for different values of $D$, ranging from 0.5 to 10 with a step 
of 0.5.
Then we calculated the maximum difference between these results and the 
value that the analytical solution assumes at the same height of the 
computation grid.
Because the gravity fields generated by a tesseroid are approximated by 
the effect of point masses, the numerical results may vary between 
computation points at same height but at different latitude or 
longitude.
That's why we choose for comparison the maximum difference between the 
results on every point of the grid and the analytical solution.

@@

Then we computed the percentage difference between the numerical model 
with its corresponding analytical solution (equation 
\ref{eq:shell-pot-linear}) for the thick and the thin spherical shell.

We can see the results for the potential, the vertical component of the 
gradient $g_z$ and the $g_{zz}$ component of the Marussi tensor on 
Figure \ref{fig:D-linear}.
We exclude the results corresponding to the other two diagonal 
components of the tensor because they are similar to the ones obtained 
for the $g_{zz}$, although they can be found on the repository. 
\todo[inline]{chequear}

>>>>

@@

We will then compute these gravitational fields on every point of the four 
grids for different values of $D$, ranging from 0.5 to 10 with a step 
of 0.5.
Then we will calculate the maximum difference between these results and the 
value that the analytical solution assumes at the same height of the 
computation grid.
Because the gravity fields generated by a tesseroid are approximated by 
the effect of point masses, the numerical results may vary between 
computation points at same height but at different latitude or 
longitude.
That's why we will choose for comparison the maximum difference between the 
results on every point of the grid and the analytical solution.

@@

We have computed the percentage difference between the numerical model 
with its corresponding analytical solution (equation 
\ref{eq:shell-pot-linear}) for the thick and the thin spherical shell 
on each of the four grids described in Table \ref{tab:grids}.
We can see the results for the potential, the vertical component of the 
gradient $g_z$ and the $g_{zz}$ component of the Marussi tensor on 
Figure \ref{fig:D-linear}.
We exclude the results corresponding to the other two diagonal 
components of the tensor because they are similar to the ones obtained 
for the $g_{zz}$, although they can be found on the repository. 
\todo[inline]{chequear}
